Eurovision Song Contest: semifinal 1, 2009

### 2025-02-11 inst/eurovision.Rmd
consistentification
distinguish hankin2017 from hankin2017_rnw
time to process without cache

---
title: "Eurovision Song Contest: semifinal 1, 2009"
output: bookdown::html_document2
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a.
The file `eurovision.txt`, used below, is copied from "Eurovision Song
Contest 2009," Wikipedia, accessed May 13, 2018.  It refers to
semi-final 1.  More documentation is given in `eurovision.Rd` [type
`help(euro2009)` at the `R` prompt].

>>>>

---
title: "Eurovision Song Contest: semifinal 1, 2009"
output: bookdown::html_document2
author: "R. K. S. Hankin"
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

 <font size=1.4px> (takes about 30 minutes to run without cache, most
of the time taken processing the `maximi` chunk)</font>

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  The file `eurovision.txt`, used below, is copied
from "Eurovision Song Contest 2009," Wikipedia, accessed May 13, 2018.
It refers to semi-final 1.  More documentation is given in
`eurovision.Rd` [type `help(euro2009)` at the `R` prompt].
